%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


  %---------------------------------------------------------
  \cventry
  {\textcolor{awesome-red}{\href{https://www.efarda.ir/}{eFarda eCommerce Company}}} % Organization
  {Fullstack Developer} % Job title
  {Tehran, Iran} % Location
  {June. 2020 - Now} % Date(s)
  {
  My Responsibilities include:
  \begin{itemize}
      \item
      Training and setting up the use of Git 
      \item
      Migrate all codes from TFS version control to Git
      \item
      Develop web APIs
      \item
      Work with bank external APIs
      \item 
      Setup CI/CD for
      \item
      Design and implement front-end of new projects
  \end{itemize}
  }
  
  %---------------------------------------------------------
  \cventry
  {Iran's national elites foundation, Shahid Ahmadi Roshan project} % Organization
  {Software Engineer} % Job title
  {Tehran, Iran} % Location
  {Jan. 2020 - Now} % Date(s)
  {
   A project funded by Iran's National Elites Foundation and supervised by \textcolor{awesome-red}{\href{http://ee.sharif.edu/~behroozi/}{Prof. Behroozi}} and \textcolor{awesome-red}{\href{http://sharif.edu/~soleymani/}{Prof. Soleymani}}.
   My Responsibilities include:
   \begin{itemize}
          \item
       Carrying out team coordination and work
       \item 
       Meeting with hospital, clinic, and laboratory managers for requirements engineering and data gathering.
       \item
      We developed a follow-up automation software that is used in the process of discharging patients and can help hospitals and clinics stay in touch with their patients and coordinate the next check ups of the patient. It also provides the patients with educational content. This system is currently being used by Sina hospital.
   \end{itemize}
  }

  %---------------------------------------------------------
  \cventry
  {Iran University of Science and Technology} % Organization
  {\textbf{Head} Teacher assistant} % Job title
  {Tehran, Iran} % Location
  {Feb. 2019 - Jul. 2019} % Date(s)
  {
    Advanced programming course supervised by \textcolor{awesome-red}{\href{https://sauleh.github.io/ap97/}{Prof. Sauleh Eetemadi}}. My responsibilities include:
    \begin{itemize}
      \item 
      Manage and coordinate TAs, Code reviewers, and other course staff.
      \item
      Design, implementation and documentation programming assignments. assignments with documentation are available via \textcolor{awesome-red}{\href{https://sauleh.github.io/ap97/assignments/}{the link}}
      \item
      Hold weekly practice classes and workshops with topics such as Git, Azure DevOps, clean code, WPF.
      \item
      Design, implementation, documentation and scoring programming exams. The mentioned exams with their corresponding answers are available via \textcolor{awesome-red}{\href{https://sauleh.github.io/ap97/assignments/}{the link}}
      \item
      More info in course home page: \textcolor{awesome-red}{\href{https://sauleh.github.io/ap97/}{https://sauleh.github.io/ap97/}}
    \end{itemize}
  }

  \cventry
  {Iran University of Science and Technology} % Organization
  {Teacher assistant} % Job title
  {Tehran, Iran} % Location
  {Oct. 2017 - Jan. 2018} % Date(s)
  {
     Advanced programming course supervised by \textcolor{awesome-red}{\href{https://sauleh.github.io/ap97/}{Prof. Sauleh Eetemadi}}. My responsibilities include:
     \begin{itemize}
      \item
      Design, implementation and documentation programming assignments.
      \item
      Hold weekly practice classes.
    \end{itemize}
  }

  \cventry
  {Sportify Project} % Organization
  {Front-end \& Back-end Developer} % Job title
  {} % Location
  {Fall 2018} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Web Programming course project}
      \item {Front-end with React.js using TypeScript.Front-end repository available in \textcolor{awesome-red}{\href{https://github.com/ali4heydari/sportify-frontend}{Github}}}
      \item {Back-end with Django framework. Back-End Repository available in \textcolor{awesome-red}{\href{https://github.com/ali4heydari/sportify-backend}{Github}}}
      \item {Implemented Google OAuth, RESTful APIs}
      \item {Design some pages in Front-End}
    \end{cvitems}
  }


  \cventry
  {Mano computer} % Organization
  {Simulate Mano computer} % Job title
  {} % Location
  {Fall 2018} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Computer architecture course project}
      \item {Implemented Mano computer architecture in proteus 8}
      \item {Repository available in \textcolor{awesome-red}{\href{https://github.com/ali4heydari/ManoComputer}{Github}}}
    \end{cvitems}
  }

  % \cventry
  % {Member} % Job title
  % {\href{fardayesabz.sharif.ir}{Fardaye-sabz Sharif charity}} % Organization
  % {Tehran, Iran} % Location
  % {2018 - Now} % Date(s)
  % {
  %   \begin{cvitems} % Description(s) of tasks/responsibilities
  %     \item {I traveled to one of the backyard areas along with other members for help.}
  %   \end{cvitems}
  % }

  % \cventry
  % {\href{http://www.kanoon.ir/}{Kanoon Farhangi Amoozesh}} % Organization
  % {Teacher \& course officer} % Job title
  % {Tehran, Iran} % Location
  % {Sep. 2017 - Feb. 2018} % Date(s)
  % {
  %   \begin{cvitems} % Description(s) of tasks/responsibilities
  %     \item {Design questions and create course materials}
  %   \end{cvitems}
  % }

  %---------------------------------------------------------
  % \cventry
  % {\href{http://calligraphers.ir/}{Association of the Calligraphers of Delijan}} % Organization
  % {Participation in calligraphy exhibition \emph{Noghte}} % Job title
  % {Delijan, Iran} % Location
  % {Mar. 2011} % Date(s)
  % {
  %   \begin{cvitems} % Description(s) of tasks/responsibilities
  %     \item {Three examples of calligraphy works were exhibited at this exhibition.}
  %   \end{cvitems}
  % }

  %---------------------------------------------------------
\end{cventries}
